Distributions of Random Variables

### 2018-09-28 DATA606/Distributions of Random Variables .Rmd
More work on DATA 606 Assignment

(a) Write down the short-hand for these two normal distributions.
(b) What are the Z-scores for Leo’s and Mary’s finishing times? What do these Z-scores tell you?
(c) Did Leo or Mary rank better in their respective groups? Explain your reasoning.
(d) What percent of the triathletes did Leo finish faster than in his group?
(e) What percent of the triathletes did Mary finish faster than in her group?
(f) If the distributions of finishing times are not nearly normal, would your answers to parts b to e change? Explain your reasoning

@@

(a) The mean height is 61.52 inches with a standard deviation of 4.58 inches. Use this information to determine if the heights approximately follow the 68-95-99.7% Rule.
(b) Do these data appear to follow a normal distribution? Explain your reasoning using the graphs provided below.

@@

>>>>

(a) Write down the short-hand for these two normal distributions.

$$ N_{\text{men 30 to 34}}(\mu=4313, \sigma=583) $$ 
$$ N_{\text{women 25 to 29}}(\mu=5261, \sigma=807) $$

(b) What are the Z-scores for Leo’s and Mary’s finishing times? What do these Z-scores tell you? **The Z-scores tell us that Mary was closer to the mean of her group and therefore was comparitively faster than Leo.**

```{r}
z_leo <- (4948-4313)/583
z_leo
```

```{r}
z_mary <- (5513-5261)/807
z_mary
```

(c) Did Leo or Mary rank better in their respective groups? Explain your reasoning.  **Mary because her Z score is lower so she is closer to the mean than Leo.**

(d) What percent of the triathletes did Leo finish faster than in his group?

```{r}
# Faster would be the area to the left of Leo's time
1 - pnorm(z_leo)
```

(e) What percent of the triathletes did Mary finish faster than in her group?

```{r}
1 - pnorm(z_mary)
```

(f) If the distributions of finishing times are not nearly normal, would your answers to parts b to e change? Explain your reasoning **No.  If it were a right skewed distribution then the proportion to the left of Mary's time would be different.**

@@

(a) The mean height is 61.52 inches with a standard deviation of 4.58 inches. Use this information to determine if the heights approximately follow the 68-95-99.7% Rule.

```{r}
heights <- c(54, 55, 56, 56, 57, 58, 58, 59, 60, 60, 60, 61, 61, 62, 62, 63, 63, 63, 64, 65, 65, 67, 67, 69, 73)

mu <- mean(heights)
sigma <- sd(heights)

for(n_sigma in 1:3){
  # Return a Boolean vector
  boolean_vector <- heights < (mu + n_sigma * sigma) & heights > (mu + -n_sigma * sigma)
  # Count the TRUEs
  n_true <- length(boolean_vector[boolean_vector==TRUE])
  # Share TRUE
  print(n_true / length(heights))
}
```

**Yes, they roughly follow the 68-95-99.7 Rule.**

(b) Do these data appear to follow a normal distribution? Explain your reasoning using the graphs provided below.

@@

**Yes.  The dots on the Q-Q plot roughly fall on the line.  This indicates the data are normally distributed.**
